---
title: "Leaflet Mapping from a Geocoded Dataset"
output:
  html_document:
    df_print: paged
---


## Leaflet Mapping A Story

In this file, I tell a story of my travels over the last 5 years (2014-2018)

```{r setup}
# set working directory
setwd("C:/Users/saraf/Desktop/CBA/Data Collection/Assignment 2")
getwd() 

suppressPackageStartupMessages({
  if (!require(stringr)){ install.packages("stringr")}; library(stringr)
  if (!require(leaflet)){ install.packages("leaflet")}; library(leaflet)
  if (!require(jsonlite)){ install.packages("jsonlite")}; library(jsonlite)
  })
```
Loading the city.list.json file and convert it into a 'regular' R dataframe.

```{r json convertion}
system.time({ df_city_list = jsonlite::fromJSON("./city.list.json") })  # 5.24 secs
dim(df_city_list)
str(df_city_list)
head(df_city_list)

#Subsetting dataset to contain data only for the specified countries

library(stringr)
df_country_city = which(str_detect(df_city_list$country, "IN|TH"))    # vector positions where country is IN or TH


df_city_sub = df_city_list[df_country_city,]     # subsetted dataset that now contains only IN or TH cities

dim(df_city_sub)

```
### Places I've travelled to in the last 5 years

Jaipur @2014 : This trip was a family vacation spanning a week in the month of October.

Bangkok @2015 : This was a trip with my 3 of my school friends. We visited a range of islands and tried some fun activities like Underwater Seawalk and Kayaking.

Bangalore @2017 : This trip was meant for a college reunion. The event was held in Marriott Hotel, Bangalore.

Manali @2017 : This was a much awaited Long weekend trip with my colleagues in the month of October.

ISB @2018 : A dream come true visit to the ISB Campus in Hyderabad.

Tirthan Valley @2018 : Hiking trip to Tirthan Valley in Himachal Pradesh.

```{r travel}
cities.travel <- c( "Jaipur", "Bangkok", "Bangalore","Manali", "Hyderabad", "Tirthan Valley")

desc.travel <- c("Family vacation @2014", "Trip with Friends @2015", "College Reunion @2017", 
               "Weekend Trip @2017", "ISB @2018","Hiking Trip @2018")

# testing geocode availability for my travels
df_travel_cities = data.frame(id=integer(), name=character(), country=character(), 
                  coord.lon=numeric(), coord.lat=numeric(), stringsAsFactors=FALSE)

df_travel_cities = df_city_sub[0,]   # Empty dataframe created

cities1 = unique(cities.travel)   # dataframe will not accept duplicate rows
cities1

# loop in the city details from the city list
for (i1 in 1:length(cities1)){
  a1 = df_city_sub[tolower(df_city_sub$name) == tolower(cities1[i1]),]; a1
  df_travel_cities = rbind(df_travel_cities, a1[1,])
}

df_travel_cities
```

### Geocoding *travel destinations*

```{r}
library(RANN)
for (i1 in 1: length(cities1))
{
  if (tolower(cities1[i1]) %in% tolower(df_city_sub$name) == FALSE) #if the city name does not exist in the json city list
  {
      lat <- as.numeric(31.7892) #Latitude for Tirthan Valley
      #lat <- as.numeric(readline(prompt = "Enter Latitude:"))
      lon <- as.numeric(76.8972) #Longitude for Tirthan Valley
      #lon <- as.numeric(readline(prompt = "Enter Longitude:"))
      country <- "IN"  #Country name for Tirthan Valley
      #country <- readLine(prompt = "Enter Country:")
      df_new <- data.frame(lon,lat)
      df_new
      df_city_sub$coord
      df_coord <- data.frame(rbind(df_new, df_city_sub$coord))
      dim(df_coord)
      df_coord[1,]
      nearest <- nn2(df_coord,k=4)[[1]]
      df_nearest_coord <- data.frame(coord.lon=numeric(),coord.lat=numeric())
      for(i in nearest[1,])
      {
          temp_coord <- df_coord[i,]
          df_nearest_coord <- rbind(df_nearest_coord,temp_coord)
      }
      df_nearest_coord
      
      #Calculating mean of the latitudes and longitudes based on the nearest coordinates
      
      df_travel_cities$coord$lon[i1] = mean(df_nearest_coord$lon)   
      df_travel_cities$coord$lat[i1] = mean(df_nearest_coord$lat)
      df_travel_cities$name[i1] = cities1[i1]
      df_travel_cities$id[i1] = i1
      df_travel_cities$country[i1] = country
  }
}

df_travel_cities
```

```{r lat-lon extraction}
# Extract latlong for target cities into DF


df1 = data.frame(city=cities.travel, desc=desc.travel)

for (i1 in 1:length(desc.travel)){
  df_city_final = which(df_travel_cities$name == cities.travel[i1])
  df1$lon[i1] = df_travel_cities$coord$lon[df_city_final]
  df1$lat[i1] = df_travel_cities$coord$lat[df_city_final]
}
df1
```
Time now to build a 'box' inside which we can call the map.  

To do this, I widen the margins of the max and min latitudes and longitudes just a little bit.

```{r inside the box} 

# for setmaxBounds() func in leaflet
lng1 = min(df1$lon) - 2; lng1
lng2 = max(df1$lon) + 2; lng2
lat1 = min(df1$lat) - 2; lat1
lat2 = max(df1$lat) + 2; lat2
```
### Using leaflet for mapping

Mapping the travel destinations

```{r leaflet}

mymap = leaflet() %>%
  
  addProviderTiles("Esri.NatGeoWorldMap") %>%    # try '?addProviderTiles' 
  
  addProviderTiles("CartoDB.DarkMatter", 
                   options = providerTileOptions(opacity = 0.5)) %>%
  
  # setView(5, 20, zoom=1) %>%
  setMaxBounds(lng1, lat1, lng2, lat2) %>%
  
  # color and weight arguments for the color and weight of the line
  addPolylines(data=df1, ~lon, ~lat, color = "white", 
               weight = 2, opacity = 1) %>%
  
  addCircleMarkers(data=df1, ~lon, ~lat,  color = "#C0392B", 
                   opacity = 0.6, radius = 3, popup = paste(df1$city, df1$desc, sep="<br>"))

mymap
```






